Re-fit

### 2022-06-28 scripts/r/04_refit/refit_sc.Rmd
♻️ - use seed when refitting models

```{r setup}
knitr::opts_knit$set(root.dir = here::here())
library(tidyverse)
library(plyr)
library(mgcv)
library(brms)
```

@@

```{r}
# LME  noun model with one fixed effect, two random effects: speaker, noun
dermatolepis_aculeatus_1_pitch_cat <- brm(
  noun_pitch_max.norms ~ effect_cat + (1 | speaker) + (1 | noun),
  data = msa_data,
  cores = 4,
  threads = threading(2, grainsize = 100), 
  backend = "cmdstanr",
  file = "./data/analyses/models/dermatolepis_aculeatus_1_pitch_cat"
)

# LME  adjective model with one fixed effect, two random effects: speaker, adjective
dermatolepis_aculeatus_2_pitch_cat <- brm(
  adj_pitch_max.norms ~ effect_cat + (1 | speaker) + (1 | adjective),
  data = msa_data,
  cores = 4,
  threads = threading(2, grainsize = 100), 
  backend = "cmdstanr",
  file = "./data/analyses/models/dermatolepis_aculeatus_2_pitch_cat"
)

# LME  phrase model with one fixed effect, two random effects: speaker, phrase
dermatolepis_aculeatus_3_pitch_cat <- brm(
  phrase_pitch_max.norms ~ effect_cat + (1 | speaker) + (1 | phrase),
  data = msa_data,
  cores = 4,
  threads = threading(2, grainsize = 100), 
  backend = "cmdstanr",
  file = "./data/analyses/models/dermatolepis_aculeatus_3_pitch_cat"
)
```

@@

```{r}
# listing all available csv files (30 participants in the production study)
trials_files <- list.files(
    path = "./osf/data/production/trial-lists/",
    pattern = ".csv", full.names = TRUE
    )

@@

# fitting the varying intercept model
# 4 chains with each 8000 post warm-up posterior samples
eriphia_laterispinis_1_mult_cat <- brm(
  bf(mvbind(mean_f0, mean_int, duration) ~
    1 + effect_cat + (1 | speaker) ) +
    set_rescor(rescor = TRUE),
  prior = priors,
  data = msa_data,
  cores = 4,
  threads = threading(2, grainsize = 100), 
  backend = "cmdstanr",
  file = "data/analyses/models/eriphia_laterispinis_1_mult_cat"
)
```

@@

```{r}
hoplostethus_macrosteus_1_dur_cat <- brm(
  durmsec ~ Observation + effect_cat + color + (1|Participant),
  data = msa_data,
  cores = 4,
  threads = threading(2, grainsize = 100), 
  backend = "cmdstanr",
  file = "data/analyses/models/hoplostethus_macrosteus_1_dur_cat"
)

hoplostethus_macrosteus_2_int_cat <- brm(
  intensity_maximum ~ Observation + effect_cat + color + (1|Participant),
  data = msa_data,
  cores = 4,
  threads = threading(2, grainsize = 100), 
  backend = "cmdstanr",
  file = "data/analyses/models/hoplostethus_macrosteus_2_int_cat"
)
```

@@

```{r}
neosilurus_omanensis_1_f0rat_cat <- brm(
  PitchRatioAtoU ~ effect_cat + (1|Participant) + (1|Adjective),
  data = msa_data,
  cores = 4,
  threads = threading(2, grainsize = 100), 
  backend = "cmdstanr",
  file = "data/analyses/models/neosilurus_omanensis_1_f0rat_cat"
)

neosilurus_omanensis_2_f0ranrat_cat <- brm(
  PitchRangeRatioAtoU ~ effect_cat + (1|Participant) + (1|Adjective),
  data = msa_data,
  cores = 4,
  threads = threading(2, grainsize = 100), 
  backend = "cmdstanr",
  file = "data/analyses/models/neosilurus_omanensis_2_f0ranrat_cat"
)

# Team also had interaction effect_cat:Condition which leads to convergence issues
# since typ:AF = 0 and atyp:ANF = 0
neosilurus_omanensis_3_f0varrat_cat <- brm(
  PitchVariationRatioAtoU ~ effect_cat + Condition + (1|Participant) + (1|Adjective),
  data = msa_data,
  cores = 4,
  threads = threading(2, grainsize = 100), 
  backend = "cmdstanr",
  file = "data/analyses/models/neosilurus_omanensis_3_f0varrat_cat"
)

neosilurus_omanensis_4_f0riserat_cat <- brm(
  PitchRiseRatio ~ effect_cat + (1|Participant) + (1|Adjective),
  data = msa_data,
  cores = 4,
  threads = threading(2, grainsize = 100), 
  backend = "cmdstanr",
  file = "data/analyses/models/neosilurus_omanensis_4_f0riserat_cat"
)

# Team also had interaction effect_cat:Condition which leads to convergence issues
# since typ:AF = 0 and atyp:ANF = 0
neosilurus_omanensis_5_srrat_cat <- brm(
  SpeechRateRatioAtoU ~ effect_cat + Condition + (1|Participant) + (1|Adjective),
  data = msa_data,
  cores = 4,
  threads = threading(2, grainsize = 100), 
  backend = "cmdstanr",
  file = "data/analyses/models/neosilurus_omanensis_5_srrat_cat"
)
```

@@

```{r}
paralichthys_undulatus_1_f0_cat <- brm(
  RangeST ~ Word.type + effect_cat + (1|Speaker) + (1|Word),
  data = msa_data,
  cores = 4,
  threads = threading(2, grainsize = 100), 
  backend = "cmdstanr",
  file = "data/analyses/models/paralichthys_undulatus_1_f0_cat"
)
```

@@

```{r}
polymetme_brevirostrum_1_dur_cat <- brm(
  Adj_Dur ~ Condition * effect_cat + effect_cat * Category + (Condition * effect_cat | Speaker) + (Condition | object) + (effect_cat | colour),
  data = msa_data,
  chains = 1,
  cores = 8,
  threads = threading(8, grainsize = 100), 
  backend = "cmdstanr",
  file = "data/analyses/models/polymetme_brevirostrum_1_dur_cat"
)
```

@@

```{r}
# The following code reads in the thirty different .csv files with the trial-level data and merges them into a single dataframe
trial_dat <- list.files(path = "./osf/data/production/trial-lists/",
                       pattern = "*.csv",
                       full.names = TRUE) %>%
  lapply(read_csv) %>%                              
  bind_rows

@@

# Fitting the lognormal model to data
saron_pictus_1_dur_cat <- brm(
  model_formula,
  data = adj,
  family = gaussian,
  prior = lognormal_priors,
  backend = "cmdstanr",
  control = list(adapt_delta = 0.99, max_treedepth = 12),
  cores = 4,
  threads = threading(2, grainsize = 100), 
  file = "data/analyses/models/saron_pictus_1_dur_cat"
)
```

@@

```{r}
trachurus_riukiuensis_1_durart_cat <- brm(
  art_dur ~ effect_cat + (1 | participant) + (1 | noun),
  data = data,
  backend = "cmdstanr",
  cores = 4,
  threads = threading(2, grainsize = 100), 
  file = "data/analyses/models/trachurus_riukiuensis_1_durart_cat"
)

trachurus_riukiuensis_2_f0art_cat <- brm(
  art_peakf0 ~ effect_cat + (1 | participant),
  data = article,
  backend = "cmdstanr",
  cores = 4,
  threads = threading(2, grainsize = 100), 
  file = "data/analyses/models/trachurus_riukiuensis_2_f0art_cat"
)

trachurus_riukiuensis_3_duradj_cat <- brm(
  adj_dur ~ effect_cat + (1|participant) + (1|noun),
  data = data,
  backend = "cmdstanr",
  cores = 4,
  threads = threading(2, grainsize = 100), 
  file = "data/analyses/models/trachurus_riukiuensis_3_duradj_cat"
)

trachurus_riukiuensis_4_f0adj_cat <- brm(
  adj_peakf0 ~ effect_cat + (1|participant) + (1|noun),
  data = adjective,
  backend = "cmdstanr",
  cores = 4,
  threads = threading(2, grainsize = 100), 
  file = "data/analyses/models/trachurus_riukiuensis_4_f0adj_cat"
)

trachurus_riukiuensis_5_f0noun_cat <- brm(
  noun_peakf0 ~ effect_cat + (1|participant) + (1|noun),
  data = noun,
  backend = "cmdstanr",
  cores = 4,
  threads = threading(2, grainsize = 100), 
  file = "data/analyses/models/trachurus_riukiuensis_5_f0noun_cat"
)
```

@@

```{r}
varanus_eulophotes_1_f0_cat <- brm(
  scaledF0 ~ effect_cat + (1|speaker),
  data = f0data_cor,
  backend = "cmdstanr",
  cores = 4,
  threads = threading(2, grainsize = 100), 
  file = "data/analyses/models/varanus_eulophotes_1_f0_cat"
)
```

>>>>

```{r setup}
knitr::opts_knit$set(root.dir = here::here())
library(tidyverse)
library(plyr)
library(mgcv)
library(brms)
my_seed = 8891
```

@@

```{r}
# LME  noun model with one fixed effect, two random effects: speaker, noun
dermatolepis_aculeatus_1_pitch_cat <- brm(
  noun_pitch_max.norms ~ effect_cat + (1 | speaker) + (1 | noun),
  data = msa_data,
  cores = 4,
  threads = threading(2, grainsize = 100), 
  backend = "cmdstanr",
  file = "./data/analyses/models/dermatolepis_aculeatus_1_pitch_cat",
  seed = my_seed
)

# LME  adjective model with one fixed effect, two random effects: speaker, adjective
dermatolepis_aculeatus_2_pitch_cat <- brm(
  adj_pitch_max.norms ~ effect_cat + (1 | speaker) + (1 | adjective),
  data = msa_data,
  cores = 4,
  threads = threading(2, grainsize = 100), 
  backend = "cmdstanr",
  file = "./data/analyses/models/dermatolepis_aculeatus_2_pitch_cat",
  seed = my_seed
)

# LME  phrase model with one fixed effect, two random effects: speaker, phrase
dermatolepis_aculeatus_3_pitch_cat <- brm(
  phrase_pitch_max.norms ~ effect_cat + (1 | speaker) + (1 | phrase),
  data = msa_data,
  cores = 4,
  threads = threading(2, grainsize = 100), 
  backend = "cmdstanr",
  file = "./data/analyses/models/dermatolepis_aculeatus_3_pitch_cat",
  seed = my_seed
)
```

@@

```{r}
# listing all available csv files (30 participants in the production study)
trials_files <- list.files(
    path = "./data/osf/production/trial-lists/",
    pattern = ".csv", full.names = TRUE
    )

@@

# fitting the varying intercept model
# 4 chains with each 8000 post warm-up posterior samples
eriphia_laterispinis_1_mult_cat <- brm(
  bf(mvbind(mean_f0, mean_int, duration) ~
    1 + effect_cat + (1 | speaker) ) +
    set_rescor(rescor = TRUE),
  prior = priors,
  data = msa_data,
  cores = 4,
  threads = threading(2, grainsize = 100), 
  backend = "cmdstanr",
  file = "data/analyses/models/eriphia_laterispinis_1_mult_cat",
  seed = my_seed
)
```

@@

```{r}
hoplostethus_macrosteus_1_dur_cat <- brm(
  durmsec ~ Observation + effect_cat + color + (1|Participant),
  data = msa_data,
  cores = 4,
  threads = threading(2, grainsize = 100), 
  backend = "cmdstanr",
  file = "data/analyses/models/hoplostethus_macrosteus_1_dur_cat",
  seed = my_seed
)

hoplostethus_macrosteus_2_int_cat <- brm(
  intensity_maximum ~ Observation + effect_cat + color + (1|Participant),
  data = msa_data,
  cores = 4,
  threads = threading(2, grainsize = 100), 
  backend = "cmdstanr",
  file = "data/analyses/models/hoplostethus_macrosteus_2_int_cat",
  seed = my_seed
)
```

@@

```{r}
neosilurus_omanensis_1_f0rat_cat <- brm(
  PitchRatioAtoU ~ effect_cat + (1|Participant) + (1|Adjective),
  data = msa_data,
  cores = 4,
  threads = threading(2, grainsize = 100), 
  backend = "cmdstanr",
  file = "data/analyses/models/neosilurus_omanensis_1_f0rat_cat",
  seed = my_seed
)

neosilurus_omanensis_2_f0ranrat_cat <- brm(
  PitchRangeRatioAtoU ~ effect_cat + (1|Participant) + (1|Adjective),
  data = msa_data,
  cores = 4,
  threads = threading(2, grainsize = 100), 
  backend = "cmdstanr",
  file = "data/analyses/models/neosilurus_omanensis_2_f0ranrat_cat",
  seed = my_seed
)

# Team also had interaction effect_cat:Condition which leads to convergence issues
# since typ:AF = 0 and atyp:ANF = 0
neosilurus_omanensis_3_f0varrat_cat <- brm(
  PitchVariationRatioAtoU ~ effect_cat + Condition + (1|Participant) + (1|Adjective),
  data = msa_data,
  cores = 4,
  threads = threading(2, grainsize = 100), 
  backend = "cmdstanr",
  file = "data/analyses/models/neosilurus_omanensis_3_f0varrat_cat",
  seed = my_seed
)

neosilurus_omanensis_4_f0riserat_cat <- brm(
  PitchRiseRatio ~ effect_cat + (1|Participant) + (1|Adjective),
  data = msa_data,
  cores = 4,
  threads = threading(2, grainsize = 100), 
  backend = "cmdstanr",
  file = "data/analyses/models/neosilurus_omanensis_4_f0riserat_cat",
  seed = my_seed
)

# Team also had interaction effect_cat:Condition which leads to convergence issues
# since typ:AF = 0 and atyp:ANF = 0
neosilurus_omanensis_5_srrat_cat <- brm(
  SpeechRateRatioAtoU ~ effect_cat + Condition + (1|Participant) + (1|Adjective),
  data = msa_data,
  cores = 4,
  threads = threading(2, grainsize = 100), 
  backend = "cmdstanr",
  file = "data/analyses/models/neosilurus_omanensis_5_srrat_cat",
  seed = my_seed
)
```

@@

```{r}
paralichthys_undulatus_1_f0_cat <- brm(
  RangeST ~ Word.type + effect_cat + (1|Speaker) + (1|Word),
  data = msa_data,
  cores = 4,
  threads = threading(2, grainsize = 100), 
  backend = "cmdstanr",
  file = "data/analyses/models/paralichthys_undulatus_1_f0_cat",
  seed = my_seed
)
```

@@

```{r}
polymetme_brevirostrum_1_dur_cat <- brm(
  Adj_Dur ~ Condition * effect_cat + effect_cat * Category + (Condition * effect_cat | Speaker) + (Condition | object) + (effect_cat | colour),
  data = msa_data,
  chains = 1,
  cores = 8,
  threads = threading(8, grainsize = 100), 
  backend = "cmdstanr",
  file = "data/analyses/models/polymetme_brevirostrum_1_dur_cat",
  seed = my_seed
)
```

@@

```{r}
# The following code reads in the thirty different .csv files with the trial-level data and merges them into a single dataframe
trial_dat <- list.files(path = "./data/osf/production/trial-lists/",
                       pattern = "*.csv",
                       full.names = TRUE) %>%
  lapply(read_csv) %>%                              
  bind_rows

@@

# Fitting the lognormal model to data
saron_pictus_1_dur_cat <- brm(
  model_formula,
  data = adj,
  family = gaussian,
  prior = lognormal_priors,
  backend = "cmdstanr",
  control = list(adapt_delta = 0.99, max_treedepth = 12),
  cores = 4,
  threads = threading(2, grainsize = 100), 
  file = "data/analyses/models/saron_pictus_1_dur_cat",
  seed = my_seed
)
```

@@

```{r}
trachurus_riukiuensis_1_durart_cat <- brm(
  art_dur ~ effect_cat + (1 | participant) + (1 | noun),
  data = data,
  backend = "cmdstanr",
  cores = 4,
  threads = threading(2, grainsize = 100), 
  file = "data/analyses/models/trachurus_riukiuensis_1_durart_cat",
  seed = my_seed
)

trachurus_riukiuensis_2_f0art_cat <- brm(
  art_peakf0 ~ effect_cat + (1 | participant),
  data = article,
  backend = "cmdstanr",
  cores = 4,
  threads = threading(2, grainsize = 100), 
  file = "data/analyses/models/trachurus_riukiuensis_2_f0art_cat",
  seed = my_seed
)

trachurus_riukiuensis_3_duradj_cat <- brm(
  adj_dur ~ effect_cat + (1|participant) + (1|noun),
  data = data,
  backend = "cmdstanr",
  cores = 4,
  threads = threading(2, grainsize = 100), 
  file = "data/analyses/models/trachurus_riukiuensis_3_duradj_cat",
  seed = my_seed
)

trachurus_riukiuensis_4_f0adj_cat <- brm(
  adj_peakf0 ~ effect_cat + (1|participant) + (1|noun),
  data = adjective,
  backend = "cmdstanr",
  cores = 4,
  threads = threading(2, grainsize = 100), 
  file = "data/analyses/models/trachurus_riukiuensis_4_f0adj_cat",
  seed = my_seed
)

trachurus_riukiuensis_5_f0noun_cat <- brm(
  noun_peakf0 ~ effect_cat + (1|participant) + (1|noun),
  data = noun,
  backend = "cmdstanr",
  cores = 4,
  threads = threading(2, grainsize = 100), 
  file = "data/analyses/models/trachurus_riukiuensis_5_f0noun_cat",
  seed = my_seed
)
```

@@

```{r}
varanus_eulophotes_1_f0_cat <- brm(
  scaledF0 ~ effect_cat + (1|speaker),
  data = f0data_cor,
  backend = "cmdstanr",
  cores = 4,
  threads = threading(2, grainsize = 100), 
  file = "data/analyses/models/varanus_eulophotes_1_f0_cat",
  seed = my_seed
)
```
